### 2024-10-21 paper/main.tex
add paper latex

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolceurws}

\title{XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler}

\author{
Li Yu \\ \\ \\ lijingyu68@gmail.com
\and
Wang Jixing \\ Science Dept.\\
                Online City, CEUR 99099 \\ jqq@ceur-ws.org
\and
Hazul \\ Research Dept.\\
                Science City, Sci 88088 \\ yvo@science.rdept.net
}

\institution{}

\begin{document}
\maketitle

\begin{abstract}
We introduce XPath Agent, a production-ready XPath programming agent tailored for web crawling tasks. A standout feature of XPath Agent is its capability to automatically program XPath queries from a set of sampled web pages. To illustrate its efficacy, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a suite of web crawling tasks. Our findings reveal that XPath Agent excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage. The well designed 2 stage pipelines makes it readily integrable into existing web crawling workflows, thereby saving time and effort in manual XPath query development.
\end{abstract}

\section{Introduction}

...

\section{Related Work}

...

\section{Methodology}

...

\subsection{ Information Extraction }

...

\subsection{ XPath Program }

...

\section{ Experiments }

...

\section{ Conclusion }

Third level headings must be flush left, initial caps and bold.
One line space before the third level heading and $1/2$ line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps and roman type.
One line space before the fourth level heading and $1/2$ line
space after the fourth level heading.

\subsection{Citations In Text}

Citations within the text should indicate the author's last name and
year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
should follow the style that you are used to using, as long as the
citation style is consistent.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{This is a sample footnote} in
the text. Place the footnotes at the bottom of the page they appear on.
Precede the footnote with a vertical rule of 2 inches (12 picas).

\subsubsection{Figures}

All artwork must be centered, neat, clean and legible. Do not use pencil
or hand-drawn artwork. Figure number and caption always appear after the
the figure. Place one line space before the figure, one line space
before the figure caption and one line space after the figure caption.
The figure caption is initial caps and each figure is numbered
consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page to avoid
splitting the figure and figure caption.

Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
The source of the figure is in file {\tt fig1.eps}.

\begin{figure}[ht]
\begin{center}
\includegraphics[height=4cm]{fig1}
\caption{Sample EPS figure }
\label{fig1}
\end{center}
\end{figure}

Below is another figure using LaTeX commands.

\begin{figure}[ht]
\begin{center}
\setlength{\unitlength}{1pt}
\footnotesize
\begin{picture}(160,80)
        \put(0,0){\framebox(160,80)[]{}}
        \put(10,35){\framebox(80,40){}}
        \put(100,20){\framebox(40,20){}}
        \put(70,10){\framebox(20,10){}}
        \put(20,5){\framebox(10,5){}}
\end{picture}
\caption{Sample Figure Caption}
\end{center}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean and legible. Do not use pencil
or hand-drawn tables. Table number and title always appear before the
table.

One line space before the table title, one line space after the table
title and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[ht]
\begin{center}
\caption{Sample Table}

\bigskip

\begin{tabular}{|l|l|r|}
\hline
A & B & 1\\ \hline
C & D & 2\\
E & F & 3\\ \hline
\end{tabular}
\end{center}
\end{table}

\subsubsection{Handling References}

Use a first level heading for the references. References follow the
acknowledgements.

\subsubsection{Acknowledgements}

Use a third level heading for the acknowledgements. All acknowledgements
go at the end of the paper.

%\bibliographystyle{alpha} 
%\bibliography{samplebib}
%inline the .bbl file directly for mailing to authors.

\begin{thebibliography}{Com79}

\bibitem[Com79]{Comer-btree}
D.~Comer.
\newblock The ubiquitous b-tree.
\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.

\bibitem[Knu73]{Knuth-vol3}
D.~E. Knuth.
\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
  Searching}.
\newblock Addison-Wesley, 1973.

\end{thebibliography}

\end{document}

### 2024-10-21 scripts/benchmarks/swde.py
Update swde.py - save and export the final evaluation csv

@@ -392,8 +392,13 @@ def eval(xpath_df: pd.DataFrame, candidates=None, sample_size=32):
 
 if __name__ == "__main__":
     xpath_df = program_xpath(
-        load_extraction_from="tmp/program_xpath",
-        save_to_dir="tmp/program_xpath_wo_q",
+        load_extraction_from="tmp/program_xpath_wo_q",
+        save_to_dir="tmp/program_xpath", # 这里面已经有文件了，第二次跑的时候，就可以直接读取，而不需要再次生成
+        ## 要评估哪个文件夹，save to 就是哪个文件夹
     )
-    df = eval(xpath_df)
+    eval_df, predictions_df = eval(xpath_df)
+
+    eval_df.to_csv("data/swde_eval.csv", index=False)
+    predictions_df.to_csv("data/swde_predictions.csv", index=False)
+
     pass

### 2024-10-25 paper/main.tex
Update main.tex
v1 of Section 2 - Related Works

@@
 \and
-Wang Jixing \\ Science Dept.\\
-                Online City, CEUR 99099 \\ jqq@ceur-ws.org
+Bryce Wang \\ Stanford University  \\ brycewang2018@gmail.com
 \and
@@
 
-\section{Introduction}
+\section{1 Introduction}
 
@@
 
-\section{Related Work}
+\section{2 Related Work}
+\subsection{2.1 LLMs and Direct Webpage Information Extraction}
+Large Language Models (LLMs) have demonstrated remarkable abilities in replicating human-like task execution, particularly in web data extraction.
+Recent advancements have enabled LLMs to process entire web pages post-crawling, facilitating direct extraction of structured information such as product details and prices.
+This method capitalizes on the LLMs' capabilities to interpret complex HTML structures without manual rule-based configurations, enhancing adaptability across dynamic web environments (Ahluwalia et al., 2024).
+However, challenges remain, particularly in ensuring factual accuracy and avoiding excessive reliance on large, computationally intensive models (Xu et al., 2024).
+Despite these hurdles, this approach offers a promising alternative to traditional web scraping, as demonstrated by models like NeuScraper, which achieve improved accuracy by integrating neural networks for direct HTML text extraction (Xu et al., 2024).
+\subsection{2.2 LLMs and Webpage Content Simplification}
+An alternative approach to direct information extraction involves simplifying web content through LLMs before targeting specific data points.
+This method filters out redundant HTML elements, reducing the size and complexity of web data while retaining the relevant information for extraction.
+By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia & Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023).
+Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).
+\subsection{2.3 LLMs and XPaths for Information Extraction}
+Generating generalizable XPath queries using LLMs has emerged as a robust method for automating web information extraction across structurally similar websites.
+This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems.
+Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
+This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (Huang et al., 2024).
+\section{3 Methodology}
 
@@
 
-\section{Methodology}
+\subsection{3.1 Information Extraction }
 
@@
 
-\subsection{ Information Extraction }
+\subsection{3.2 XPath Program }
 
@@
 
-\subsection{ XPath Program }
+\section{4 Experiments }
 
@@
 
-\section{ Experiments }
-
-...
-
-\section{ Conclusion }
+\section{5 Conclusion }
 

### 2024-10-25 paper/main.tex
Update main.tex
Section 2 -Related Works v2

@@
 
-\section{1 Introduction}
+\section{Introduction}
 
@@
 
-\section{2 Related Work}
-\subsection{2.1 LLMs and Direct Webpage Information Extraction}
+\section{Related Work}
+\subsection{LLMs and Direct Webpage Information Extraction}
 Large Language Models (LLMs) have demonstrated remarkable abilities in replicating human-like task execution, particularly in web data extraction.
@@
 Despite these hurdles, this approach offers a promising alternative to traditional web scraping, as demonstrated by models like NeuScraper, which achieve improved accuracy by integrating neural networks for direct HTML text extraction (Xu et al., 2024).
-\subsection{2.2 LLMs and Webpage Content Simplification}
+\subsection{LLMs and Webpage Content Simplification}
 An alternative approach to direct information extraction involves simplifying web content through LLMs before targeting specific data points.
@@
 Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).
-\subsection{2.3 LLMs and XPaths for Information Extraction}
+\subsection{LLMs and XPaths for Information Extraction}
 Generating generalizable XPath queries using LLMs has emerged as a robust method for automating web information extraction across structurally similar websites.
@@
 This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (Huang et al., 2024).
-\section{3 Methodology}
+\section{Methodology}
 
@@
 
-\subsection{3.1 Information Extraction }
+\subsection{Information Extraction }
 
@@
 
-\subsection{3.2 XPath Program }
+\subsection{XPath Program }
 
@@
 
-\section{4 Experiments }
+\section{Experiments }
 
@@
 
-\section{5 Conclusion }
+\section{Conclusion }
 

### 2024-10-28 paper/main.tex
update paper

@@
 To illustrate its efficacy, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a suite of web crawling tasks.
-Our findings reveal that XPath Agent excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage.
+Our findings reveal that XPath Agent excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
 The well designed 2 stage pipelines makes it readily integrable into existing web crawling workflows, thereby saving time and effort in manual XPath query development.
@@
 
-...
+Web scraping \cite{khder2021web} automates data extraction from websites, vital for modern fields like Business Intelligence.
+It excels in gathering structured data from unstructured sources like HTML, especially when machine-readable formats are unavailable.
+Web scraping provides real-time data, such as pricing from retail sites, and can offer insights into illicit activities like darknet drug markets.
 
@@
 
-%\bibliographystyle{alpha} 
-%\bibliography{samplebib}
-%inline the .bbl file directly for mailing to authors.
-
-\begin{thebibliography}{Com79}
-
-\bibitem[Com79]{Comer-btree}
-D.~Comer.
-\newblock The ubiquitous b-tree.
-\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
-
-\bibitem[Knu73]{Knuth-vol3}
-D.~E. Knuth.
-\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
-  Searching}.
-\newblock Addison-Wesley, 1973.
-
-\end{thebibliography}
+\bibliographystyle{plain} 
+\bibliography{refs}
 

### 2024-10-28 paper/main.tex
paper: add introduction

@@
 
+The advent of HTML5 \cite{TABARES2021101529} has introduced significant complexities to automated web scraping, exacerbating issues of fragmentation and protocol diversity that have long challenged the development of web standards.
+These complexities stem from the enhanced capabilities and dynamic nature of HTML5, which require more sophisticated methods to accurately extract and interpret data.
+As traditional web scraping techniques struggle to keep pace with these advancements, there is a growing need for innovative solutions to navigate the intricacies of modern web technologies.
+
+The development of Large Language Models (LLM) has emerged as a promising avenue.
+LLMs, with their advanced natural language processing capabilities, offer a new paradigm for understanding and interacting with web content.
+AutoWebGLM\cite{lai2024autowebglmlargelanguagemodelbased} demonstrated significant advancements in addressing the complexities of real-world web navigation tasks, particularly in simplifying HTML data representation to enhancing it's capability.
+By leveraging reinforcement learning and rejection sampling, AutoWebGLM enhanced its ability to comprehend webpages, execute browser operations, and efficiently decompose tasks.
+
+Instead of fine-tuning LLMs, AutoScraper\cite{huang2024autoscraperprogressiveunderstandingweb} adopt a simplified technique which involves traversing the webpage and constructing a final XPath using generated action sequences.
+By focusing on the hierarchical structure of HTML and leveraging similarities across different web pages, its significantly reduces the complexity and computational overhead.
+
+Scrolling, navigating, back and forward through the webpage to generate XPath queries is a nature way for human. But for LLM, this process is time-consuming and computationally expensive.
+
+\subsection{Motivation}
+
+We assuming there are 3 core reasons why LLMs are not efficient in generating XPath queries.
+Firstly, LLMs are not designed to generate XPath queries.
+They are designed to understand and generate human-like text.
+Secondly, web pages are lengthy and complex, full of task unrelated information.
+Those information distract the LLMs from generating the correct XPath queries.
+Thirdly, a good XPath query should be generalizable across different web pages.
+However, LLMs are context limited, which means they can only generate XPath queries based on the context they have seen.
+
+Based on the above insights, we propose a novel approach to generate XPath queries using LLMs.
+Our approach is designed to be efficient, accurate, and generalizable.
+We aim to reduce the number of steps required to generate a well-crafted XPath query, reduce the computational overhead, and improve the generalizability of the XPath queries generated by LLMs.
+
+In order to increase the efficiency of XPath query generation, we also employed LangGraph.
+Which is a graph-based tool set which we can define the whole pipeline in a graph-based manner and execute it in parallel.
+Which significantly reduce the time required to generate XPath queries.
+
+\subsection{Our Contributions}
+
 \section{Related Work}
@@
 Despite these hurdles, this approach offers a promising alternative to traditional web scraping, as demonstrated by models like NeuScraper, which achieve improved accuracy by integrating neural networks for direct HTML text extraction (Xu et al., 2024).
+
 \subsection{LLMs and Webpage Content Simplification}
@@
 This method filters out redundant HTML elements, reducing the size and complexity of web data while retaining the relevant information for extraction.
-By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia & Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023).
+By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia \& Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023).
 Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).
+
 \subsection{LLMs and XPaths for Information Extraction}
@@
 
-Citations within the text should indicate the author's last name and
-year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
-should follow the style that you are used to using, as long as the
-citation style is consistent.
+...
 
@@
 
-Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
-The source of the figure is in file {\tt fig1.eps}.
-
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[height=4cm]{fig1}
-\caption{Sample EPS figure }
-\label{fig1}
-\end{center}
-\end{figure}
-
 Below is another figure using LaTeX commands.
-
-\begin{figure}[ht]
-\begin{center}
-\setlength{\unitlength}{1pt}
-\footnotesize
-\begin{picture}(160,80)
-        \put(0,0){\framebox(160,80)[]{}}
-        \put(10,35){\framebox(80,40){}}
-        \put(100,20){\framebox(40,20){}}
-        \put(70,10){\framebox(20,10){}}
-        \put(20,5){\framebox(10,5){}}
-\end{picture}
-\caption{Sample Figure Caption}
-\end{center}
-\end{figure}
 
@@
 
+% \addbibresource{refs.bib}
 \bibliographystyle{plain} 

### 2024-10-28 paper/main.tex
add contribution

@@
 \author{
-Li Yu \\ \\ \\ lijingyu68@gmail.com
+Li Yu \\ \\ lijingyu68@gmail.com
 \and
@@
 
-Scrolling, navigating, back and forward through the webpage to generate XPath queries is a nature way for human. But for LLM, this process is time-consuming and computationally expensive.
+Scrolling, navigating, back and forward through webpages to program XPath queries is a nature way for human.
+But for LLM, this process is time-consuming and computationally expensive.
+We expect LLM can do better and efficient.
 
@@
 Firstly, LLMs are not designed to generate XPath queries.
-They are designed to understand and generate human-like text.
 Secondly, web pages are lengthy and complex, full of task unrelated information.
 Those information distract the LLMs from generating the correct XPath queries.
-Thirdly, a good XPath query should be generalizable across different web pages.
-However, LLMs are context limited, which means they can only generate XPath queries based on the context they have seen.
+Thirdly, LLMs are context limited.
+A good XPath query should be generalizable across different web pages.
+However, LLMs can only generate XPath queries based on the context they have seen.
+So, a shorter and more task-related context is more likely to generate a better XPath query.
 
 Based on the above insights, we propose a novel approach to generate XPath queries using LLMs.
-Our approach is designed to be efficient, accurate, and generalizable.
 We aim to reduce the number of steps required to generate a well-crafted XPath query, reduce the computational overhead, and improve the generalizability of the XPath queries generated by LLMs.
@@
 \subsection{Our Contributions}
+
+We address each of the above motivations and make the following main contributions:
+
+\begin{enumerate}
+  \item We designed a two stage pipeline, which we can employ a week LLM to extract target information. And a stronger LLM to program XPath.
+  \item We proposed a simple way to prune the web page, which can reduce the complexity of the web page and make the LLM focus on the target information.
+  \item We discovered a cue text that share context between two stage significantly improve the performance of the XPath programming agent.
+  \item We benchmarked our approach against a state-of-the-art XPath programming agent across a suite of web crawling tasks.
+Our findings reveal that our approach excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
+\end{enumerate}
 

### 2024-10-30 feilian/chains/program_xpath_chain.py
Update program_xpath_chain.py
from langchain_anthropic import ChatAnthropic

@@ -4,6 +4,7 @@ from functional import compose
 from operator import itemgetter
 from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 
 from feilian.prompts import (
     XPATH_PROGRAM_PROMPT_HISTORY_CN,
@@ -19,7 +20,7 @@ def _create_program_xpath_chain():
             return_objects=True,
         )
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( #ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
         model_kwargs={

### 2024-10-30 feilian/chains/program_xpath_chat.py
Update program_xpath_chat.py
from langchain_anthropic import ChatAnthropic

@@ -9,6 +9,7 @@ from langchain_core.chat_history import BaseChatMessageHistory
 from langchain_community.chat_message_histories import ChatMessageHistory
 from langchain_core.runnables.history import RunnableWithMessageHistory
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 
 lang = os.environ.get("PROMPT_LANG", "cn")
 
@@ -92,7 +93,7 @@ def create_program_xpath_chat_chain():
             return ""
         return result.get("xpath", "")
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_PROGRAM_XPATH_MODEL", "deepseek-chat"),
         temperature=0,
         max_tokens=512,

### 2024-10-30 feilian/agents/table_agent.py
Anthropic

@@ -10,6 +10,7 @@ from langgraph.graph import StateGraph, START, END
 from langgraph.constants import Send
 from enum import Enum
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 from minify_html import minify
 from langgraph.checkpoint.sqlite import SqliteSaver
 
@@ -122,7 +123,7 @@ def get_tree(snippet: Snippet, compact: bool = True) -> etree._Element:
 
 
 def _create_table_extraction_chain():
-    llm = ChatOpenAI(
+    llm = ChatOpenAI(   #ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0.1,
         model_kwargs={
@@ -135,7 +136,7 @@ def _create_table_extraction_chain():
 
 
 def _create_program_xpath_chain():
-    llm = ChatOpenAI(
+    llm = ChatOpenAI(  #ChatAnthropic
         model="deepseek-coder",
         temperature=0.1,
         model_kwargs={
@@ -151,7 +152,7 @@ def _create_program_xpath_chain():
 
 
 def _create_question_conversion_chain():
-    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0.1)
+    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0.1) # ChatAnthropic
     return QUESTION_CONVERSION_COMP_CN | llm
 
 

### 2024-10-30 feilian/chains/critic_xpath_chain.py

@@ -4,6 +4,7 @@ from functional import compose
 from operator import itemgetter
 from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 
 
 def _create_critic_xpath_chain():
@@ -13,7 +14,7 @@ def _create_critic_xpath_chain():
             return_objects=True,
         )
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )

### 2024-10-30 feilian/chains/information_extraction_chain.py

@@ -4,6 +4,7 @@ import json_repair
 from operator import itemgetter
 from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
+from langchain_anthropic import ChatAnthropic
 
 lang = os.environ.get("PROMPT_LANG", "cn")
 
@@ -24,7 +25,7 @@ def json_parser(response):
 
 
 def create_information_extraction_chain(cue=False):
-    llm = ChatOpenAI(model=os.environ.get("OPENAI_IE_MODEL"), temperature=0)
+    llm = ChatOpenAI(model=os.environ.get("OPENAI_IE_MODEL"), temperature=0) # ChatAnthropic
     if cue:
         template_file = f"feilian/prompts/{lang}/information_extraction_with_cue.jinja2"
         example = {
@@ -64,7 +65,7 @@ def _create_best_composition_chain():
 
         return choices
 
-    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0)
+    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0) # ChatAnthropic
     template_file = f"feilian/prompts/{lang}/best_composition.yaml"
     prompt = PromptTemplate.from_file(template_file)
     return prompt | llm | parser

### 2024-10-30 feilian/chains/program_css_selector_chain.py

@@ -4,6 +4,7 @@ from functional import compose
 from operator import itemgetter
 from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 
 
 def create_cot_program_css_selector_s2():
@@ -16,7 +17,7 @@ def create_cot_program_css_selector_s2():
         json_str = json_str.split("```")[0].strip()
         return json_repair.repair_json(json_str, return_objects=True)
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI(  # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )
@@ -43,7 +44,7 @@ def create_cot_program_css_selector_s1():
         json_str = json_str.split("```")[0].strip()
         return json_repair.repair_json(json_str, return_objects=True)
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )

### 2024-10-30 feilian/chains/program_xpath_chain.py

@@ -48,7 +48,7 @@ def _create_cot_program_xpath_s3_chain():
         json_str = json_str.split("```")[0].strip()
         return json_repair.repair_json(json_str, return_objects=True)
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )
@@ -81,7 +81,7 @@ def create_cot_program_xpath_s2():
         json_str = json_str.split("```")[0].strip()
         return json_repair.repair_json(json_str, return_objects=True)
 
-    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0)
+    llm = ChatOpenAI(model=os.getenv("OPENAI_MODEL"), temperature=0) # ChatAnthropic
     template_file = f"feilian/prompts/{lang}/program_xpath_cot_s2.yaml"
     return (
         {
@@ -106,7 +106,7 @@ def create_cot_program_xpath_s1():
         json_str = json_str.split("```")[0].strip()
         return json_repair.repair_json(json_str, return_objects=True)
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )

### 2024-10-30 feilian/chains/xpath_rewrite_chain.py

@@ -2,6 +2,7 @@ import os
 import json_repair
 from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
+#from langchain_anthropic import ChatAnthropic
 
 lang = os.environ.get("PROMPT_LANG", "cn")
 
@@ -38,7 +39,7 @@ def create_xpath_rewrite_chain():
         result = json_repair.loads(text) or {}
         return result.get("xpath", "")
 
-    llm = ChatOpenAI(
+    llm = ChatOpenAI( # ChatAnthropic
         model=os.getenv("OPENAI_MODEL"),
         temperature=0,
     )

### 2024-10-30 feilian/dataset_tools.py

@@ -9,6 +9,7 @@ from tqdm import tqdm
 from collections import defaultdict
 from minify_html import minify
 from langchain_openai.chat_models import ChatOpenAI
+#from langchain_anthropic.chat_models import ChatAnthropic
 from langchain_core.prompts import ChatPromptTemplate
 
 from feilian.soup_tools import get_node_contain_text, get_common_ancestor, clean_html
@@ -153,7 +154,7 @@ def swde__construct_question(file_path: str):
     """
 
     # construct question using langchain
-    llm = ChatOpenAI(model="deepseek-chat", temperature=0.1)
+    llm = ChatOpenAI(model="deepseek-chat", temperature=0.1) # ChatAnthropic    
     template = ChatPromptTemplate.from_messages([("human", QUESTION_CONSTRUCTION_EN)])
     chain = template | llm
 

### 2024-11-04 feilian/chains/information_extraction_chain.py
change default lang from cn to en

@@ -6,7 +6,7 @@ from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
 from langchain_anthropic import ChatAnthropic
 
-lang = os.environ.get("PROMPT_LANG", "cn")
+lang = os.environ.get("PROMPT_LANG", "en")
 
 
 def json_parser(response):
@@ -52,7 +52,7 @@ def create_information_extraction_chain(cue=False):
 
 
 def _create_best_composition_chain():
-    lang = os.environ.get("PROMPT_LANG", "cn")
+    lang = os.environ.get("PROMPT_LANG", "en")
 
     def parser(response):
         if lang == "cn":

### 2024-11-04 feilian/chains/program_xpath_chain.py

@@ -66,7 +66,7 @@ def _create_cot_program_xpath_s3_chain():
 
 
 def create_cot_program_xpath_s2():
-    lang = os.environ.get("PROMPT_LANG", "cn")
+    lang = os.environ.get("PROMPT_LANG", "en")
 
     def parser(response):
         if lang == "cn":

### 2024-11-04 feilian/chains/program_xpath_chat.py

@@ -11,7 +11,7 @@ from langchain_core.runnables.history import RunnableWithMessageHistory
 from langchain_openai import ChatOpenAI
 #from langchain_anthropic import ChatAnthropic
 
-lang = os.environ.get("PROMPT_LANG", "cn")
+lang = os.environ.get("PROMPT_LANG", "en")
 
 program_xpath_chat_system = PromptTemplate.from_file(
     "feilian/prompts/en/program_xpath_chat_system.jinja2",

### 2024-11-04 feilian/chains/xpath_rewrite_chain.py

@@ -4,7 +4,7 @@ from langchain_core.prompts import PromptTemplate
 from langchain_openai import ChatOpenAI
 #from langchain_anthropic import ChatAnthropic
 
-lang = os.environ.get("PROMPT_LANG", "cn")
+lang = os.environ.get("PROMPT_LANG", "en")
 
 
 def rindex(lst, value):

### 2024-11-04 paper/main.tex
update paper

@@
 
-We address each of the above motivations and make the following main contributions:
+We based each of the above motivations and make the following contributions:
 
 \begin{enumerate}
-  \item We designed a two stage pipeline, which we can employ a week LLM to extract target information. And a stronger LLM to program XPath.
+  \item We designed a two stage pipeline, which we can employ a weaker LLM to extract target information. And a stronger LLM to program XPath.
   \item We proposed a simple way to prune the web page, which can reduce the complexity of the web page and make the LLM focus on the target information.
-  \item We discovered a cue text that share context between two stage significantly improve the performance of the XPath programming agent.
-  \item We benchmarked our approach against a state-of-the-art XPath programming agent across a suite of web crawling tasks.
+  \item We discovered that extracted cue texts from 1st stage significantly improve the performance of the 2nd stage.
+  \item We benchmarked our approach against a state-of-the-art same purpose agent across a suite of web crawling tasks.
 Our findings reveal that our approach excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.

### 2024-11-04 feilian/statistical_analysis.py

@@ -43,7 +43,7 @@ def swde__stats_token_row(row):
     html_file_path = os.path.join(SWDE_DATA_ROOT, row["file_path"])
     html = open(html_file_path).read()
     tree = parse_html(html)
-    etree_clean_html(tree)
+    etree_clean_html(tree, True)
     cleaned_html = minify(to_string(tree), keep_closing_tags=True)
 
     row["raw_tokens"] = tokenizer(html)
@@ -52,52 +52,69 @@ def swde__stats_token_row(row):
     return row
 
 
-def swde__stats_token(dataset_file_path: str):
-    from pandarallel import pandarallel
-
-    pandarallel.initialize(progress_bar=True, nb_workers=4)
-
-    df = pd.read_parquet(dataset_file_path)
-
-    # sample 256 per group, group by category, site
-    df = df.groupby(["category", "site"]).apply(
-        lambda x: x.sample(min(len(x), 256), replace=False)
-    )
-
-    # remove index
-    df.reset_index(drop=True, inplace=True)
-
-    df = df.parallel_apply(swde__stats_token_row, axis=1)
-    df.to_csv("data/swde_token_stats.csv")
+def _bin_fn(x):
+    return x // 4000 * 4000
 
 
 def swde__plot_token_dist(
     dataset_file_path: str,
-    group_cols: list = ["category", "site"],
     target_col: str = "cleaned_tokens",
+    sample_size: int = 128,
 ):
-    from plotly.subplots import make_subplots
     import plotly.graph_objects as go
+    import plotly.express as px
 
+    # read & sample
     df = pd.read_csv(dataset_file_path, index_col=0)
-    pairs = df[group_cols].groupby(group_cols).nunique().index
-    n_cols = 8
-    n_rows = len(pairs) // n_cols + 1
+    df = df.groupby(["category", "site"]).apply(
+        lambda x: x.sample(min(len(x), sample_size), replace=False)
+    )
+    df.reset_index(drop=True, inplace=True)
 
-    fig = make_subplots(
-        rows=n_rows, cols=n_cols, subplot_titles=[f"{pair}" for pair in pairs]
+    # count tokens
+    df = df.apply(swde__stats_token_row, axis=1)
+    df["token_cat"] = df["raw_tokens"].apply(_bin_fn)
+    group_df = (
+        df.groupby("token_cat")["raw_tokens", "cleaned_tokens"].mean().astype(int)
     )
 
-    for i, pair in enumerate(pairs):
[…]

### 2024-11-04 paper/html_condenser.py
update paper, add core algorithm

@@ -1,0 +1,30 @@
+# 伪代码
+from collections import defaultdict
+
+
+# input:
+#     root: html root node
+#     target_texts: list of target texts to keep
+#     d: distance between two texts
+# output:
+#     root: condensed html root node
+target_texts = []
+distances = defaultdict(int)
+keep_elements = defaultdict(list)
+for ele, text in itertext(root):
+    for target_text in target_texts:
+        distance = d(text, target_text)
+        if distance < distances[text]:
+            distances[text] = distance
+            keep_elements[text] = [get_xpath(ele)]
+        elif distance == distances[text]:
+            keep_elements[text].append(get_xpath(ele))
+
+includes = concat(keep_elements.values())
+for xpath, ele in iter_elements(root):
+    is_parent = any([x.startswith(xpath) for x in includes])
+    is_inside = any([xpath.startswith(x) for x in includes])
+    if not is_in_path and not is_contained:
+        if any([x.startswith(parent_xpath(xpath)) for x in includes]):
+            remove_children(ele)
+            add_text(ele, "...")

### 2024-11-04 paper/information_extraction_sanitizer.py

@@ -1,0 +1,17 @@
+if not root_node:
+    return []
+
+left_stack = [root_node]
+right_stack = []
+
+while left_stack:
+    node = left_stack.pop()
+    right_stack.append(node)
+    left_stack += list(node.iterchildren())
+
+while right_stack:
+    node = right_stack.pop()
+    if is_invisiable_or_no_text(node):
+        node.getparent().remove(node)
+    else:
+        node.remove_attributes()

### 2024-11-05 paper/main.tex
update paper, add core algorithm
update paper

@@
 \usepackage{twocolceurws}
+\usepackage[ruled,vlined]{algorithm2e}
+\usepackage{graphicx}
+\usepackage{adjustbox}
+\usepackage{caption} % 引入 caption 包
+
+\captionsetup[figure]{skip=10pt} % 设置 caption 的下边距为 10pt
 
@@
 This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (Huang et al., 2024).
+
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=1\textwidth]{./workflow.png}
+  \caption{XPath Agent of two stages pipeline.
+The first stage is Information Extraction, which extracts target information and cue text from sanitized web pages (the red are sanitized).
+The second stage is XPath Programming, which generates XPath queries based on condensed html (the green are kept) and generated XPath.}
+  \label{fig:workflow}
+  \vspace{20pt} % 手动插入 20pt 的垂直间距
+\end{figure*}
+
 \section{Methodology}
 
-...
+In this section, we present the methodology of our approach, which consists of two stages: Information Extraction (IE) and XPath Programming.
+The IE stage extracts target information from sanitized web pages, while the XPath Programming stage generates XPath queries based on the condensed html and extracted information.
+\ref{fig:workflow} illustrates the two-stage pipeline of XPath Agent.
+For each stage, we provide a detailed description of the process and the algorithms used.
 
-\subsection{Information Extraction }
+\subsection{Information Extraction with Cue Text}
 
-...
+The Information Extraction (IE) stage aims to extract target information.
+Not like traditional IE, we discovered 2 key insights.
+Firstly, we prompt the LLM to not only extract questioned information but also extract cue texts.
+Cue texts are the texts that are close to the target information and can help the LLM to generate better XPath queries.
+Secondly, we sanitize the web page before feeding it to the LLM.
+Sanitizing the web page can reduce the complexity of the web page and make the LLM focus on the target information.
 
-\subsection{XPath Program }
+\begin{algorithm}
+  \SetAlgoLined
+  \caption{IE HTML Sanitizer}
+  \KwIn{Root node of HTML tree $root\_node$}
+  \KwOut{Sanitized HTML tree}
 
-...
+  $left\_stack \gets [root\_node]$\;
+  $right\_stack \gets []$\;
+
+  \While{$left\_stack$ is not empty}{
+      $node \gets left\_stack.pop()$\;
+      $right\_stack.append(node)$\;
+      $left\_stack \gets left\_stack + list(node.iterchildren())$\;
+  }
+
+  \While{$right\_stack$ is not empty}{
+      $node \gets right\_stack.pop()$\;
+      \If{$is\_invisiable\_or\_no\_text(node)$}{
+          $node.getparent().remove(node)$\;
+      }
+      \Else{
+          $node.remove\_attributes()$\;
+      }
+  }
+\end{algorithm}
+
+\subsection{XPath Program}
+
+\begin{algorithm}
+  \SetAlgoLined
+  \caption{HTML Condenser}
+  \KwIn{
+      $root$: HTML root node\;
+      $target\_texts$: List of target texts to keep\;
+      $d$: Distance function between two texts\;
+  }
+  \KwOut{
+      $root$: Condensed HTML root node\;
+  }
+
+  $target\_texts \gets []$\;
+  $distances \gets \{\}$\;
+  $eles \gets \{\}$\;
+
+  \ForEach{$ele, text$ in \texttt{iter\_with\_text}($root$)}{
+      \ForEach{$target\_text$ in $target\_texts$}{
+          $distance \gets d(text, target\_text)$\;
+          \If{$distance < distances[text]$}{
+              $distances[text] \gets distance$\;
+              $eles[text] \gets [\texttt{get\_xpath}($ele$)]$\;
+          }
+          \ElseIf{$distance == distances[text]$}{
+              $eles[text].\texttt{append}(\texttt{get\_xpath}($ele$))$\;
+          }
+      }
+  }
+
+  $targets \gets \texttt{concat}(\texttt{values}(eles))$\;
+  \ForEach{$xpath, ele$ in \texttt{iter\_with\_xpath}($root$)}{
+    \If{\texttt{is\_outside}($xpath$, $targets$)}{
+      \texttt{remove\_children}(ele)\;
+      \texttt{replace\_text\_to}(ele, "...")\;
+    }
+  }
+
+\end{algorithm}
 

### 2024-11-05 scripts/test_tool/segment_preview/main.py

@@ -1,0 +1,139 @@
+# 该脚本的目的：
+# 1. 收集正确的 XPath
+# 2. 通过正确的 XPath 在页面中高亮显示对应的元素，然后用来判断
+import pandas as pd
+import os
+import json
+import html
+from playwright.sync_api import sync_playwright
+
+DATA_ROOT = "data/swde"
+
+
+def normalize(text):
+    import re
+
+    # print(text_list)
+    text = html.unescape(text)
+    text = text.replace("&lt;", "<")
+    text = text.replace("&gt;", ">")
+    text = text.replace("&amp;", "&")
+    text = text.replace("&quot;", '"')
+    text = text.replace("&#39;", "'").replace("&apos;", "'")
+    text = text.replace("&#150;", "–")
+    text = text.replace("&nbsp;", " ")
+    text = text.replace("&#160;", " ")
+    text = text.replace("&#039;", "'")
+    text = text.replace("&#34;", '"')
+    text = text.replace("&reg;", "®")
+    text = text.replace("&rsquo;", "’")
+    text = text.replace("&#8226;", "•")
+    text = text.replace("&ndash;", "–")
+    text = text.replace("&#x27;", "'")
+    text = text.replace("&#40;", "(")
+    text = text.replace("&#41;", ")")
+    text = text.replace("&#47;", "/")
+    text = text.replace("&#43;", "+")
+    text = text.replace("&#035;", "#")
+    text = text.replace("&#38;", "&")
+    text = text.replace("&eacute;", "é")
+    text = text.replace("&frac12;", "½")
+    # text = text.replace("  ", " ")
+    # text = re.sub(r"\s+", "", text)
+    return text.strip()
+
+
+def label_xpath_row(page, row):
+    full_url = os.path.abspath(os.path.join(DATA_ROOT, row["file_path"]))
+
+    page.goto(f"file://{full_url}")
+
+    # highlight ground truth
+    ground_truth = json.loads(row["attributes"])
+    result = {}
+    prev_elements = []
+    for k, v in ground_truth.items():
+        for ele in prev_elements:
+            ele.evaluate("node => node.style.backgroundColor = ''")
+
+        for text in v:
+            normalized_text = normalize(text)
+            count = page.get_by_text(normalized_text).count()
+            for i in range(count):
+                ele = page.get_by_text(normalized_text).nth(i)
+                if ele.is_visible():
+                    ele.evaluate("node => node.style.backgroundColor = 'yellow'")
[…]

### 2024-11-05 paper/main.tex
update paper 3.1

@@
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage{graphicx}
 \usepackage{adjustbox}
@@
 The first stage is Information Extraction, which extracts target information and cue text from sanitized web pages (the red are sanitized).
-The second stage is XPath Programming, which generates XPath queries based on condensed html (the green are kept) and generated XPath.}
+The second stage is XPath Programming, which generates XPath queries based on condensed html (the greens are target nodes) and generated XPath.}
   \label{fig:workflow}
@@
 The IE stage extracts target information from sanitized web pages, while the XPath Programming stage generates XPath queries based on the condensed html and extracted information.
-\ref{fig:workflow} illustrates the two-stage pipeline of XPath Agent.
+Figure \ref{fig:workflow} illustrates the two-stage pipeline of XPath Agent.
 For each stage, we provide a detailed description of the process and the algorithms used.
@@
 Not like traditional IE, we discovered 2 key insights.
-Firstly, we prompt the LLM to not only extract questioned information but also extract cue texts.
-Cue texts are the texts that are close to the target information and can help the LLM to generate better XPath queries.
-Secondly, we sanitize the web page before feeding it to the LLM.
-Sanitizing the web page can reduce the complexity of the web page and make the LLM focus on the target information.
+Firstly, we prompt the LLM to not only extract questioned information but also include cue texts.
+Secondly, we sanitized the web page to reduce the complexity of the web page and make the LLM focus on the target information.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.5\textwidth]{./ie_token_stats.eps}
+  \caption{Token Stats Analysis with Algorithm 1. As page size grow, the size after sanitization increased slowly (sampled 128 pages for each category from SWDE dataset, around 10k pages totally).}
+  \label{fig:ie_token_stats}
+\end{figure}
+
+Cue texts are the indicative texts that signals the upcoming target information.
+For example, for "price: \$100.00", the cue text is "price:".
+Those texts are important in some case, especially when no way or hard to directly programming XPath queries to extract target information "\$100.00".
+In such case, treat "price:" as an anchor, using XPath's ancestor, sibling, or descendant axis traverse to the target information is the only way.
+In order to let the context still be condensed, we prompt LLM to response cue texts simultaneously.
+
+Sanitizing web page is a process to remove unnecessary information from a page.
+In HTML, the most meaningful parts are texts and tags.
+The texts are the target information we want to extract, and the tags are the structure of the web page which tells the relationship between texts especially the priority of which answer is more likely to be the target information.
+The purpose of sanitizing the web page is to reduce the complexity of the web page and make the LLM focus on the target information.
+We designed an algorithm to sanitize the web page, which is shown in Algorithm \ref{alg:sanitizer}.
+
+The algorithm 1 traverse the HTML tree in a depth-first manner.
+It removes the invisible or empty nodes and removes all attributes.
+It's efficient and can be easily implemented in any programming language.
+In our sampled web pages, the algorithm can reduce the size of the web page by 80\%~90\% on average.
+
+In our implementation, we prompt LLM to extract all information at once on a single page with JSON format.
+So, multiple fields can be extracted at the same time.
+Multiple values for a single field might be extracted.
+We simply treat all extracted values are relevant and passing them to the next stage.
 
@@
   \caption{IE HTML Sanitizer}
+  \label{alg:sanitizer}
   \KwIn{Root node of HTML tree $root\_node$}

### 2024-11-05 paper/main.tex
simple update

@@
 The algorithm 1 traverse the HTML tree in a depth-first manner.
-It removes the invisible or empty nodes and removes all attributes.
+It removes the invisible or empty nodes, and all attributes.
 It's efficient and can be easily implemented in any programming language.
-In our sampled web pages, the algorithm can reduce the size of the web page by 80\%~90\% on average.
+In our sampled web pages, the algorithm can help us reduce the size of the web page to 10\%~20\% on average.
 
@@
 Multiple values for a single field might be extracted.
-We simply treat all extracted values are relevant and passing them to the next stage.
+In this case, We simply treat all extracted values are relevant and passing them to the next stage.
 

### 2024-11-05 paper/main.tex
Update main.tex: related works - generative information extraction
generative information extraction

@@
 
-\subsection{LLMs and Webpage Content Simplification}
-An alternative approach to direct information extraction involves simplifying web content through LLMs before targeting specific data points.
-This method filters out redundant HTML elements, reducing the size and complexity of web data while retaining the relevant information for extraction.
-By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia \& Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023).
-Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).
+\subsection{Generative Information Extraction}
+The use of large models for information extraction is commonly referred to as generative information extraction, which leverages large language models (LLMs) to extract structured knowledge from text, such as entities, relations, and events, providing an alternative to traditional discriminative methods (Xu et al., 2024).
+Unlike traditional models, LLMs directly generate structured information and perform well even in low-resource settings, supporting multitasking formats.
+IE tasks are generally categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with each task's performance and typical models rigorously compared (Xu et al., 2024).
+Recent universal IE frameworks employ both natural language-based (NL-LLMs) and code-based (Code-LLMs) approaches.
+NL-LLMs, such as UIE and InstructUIE, use natural language prompts to generate structured information, whereas Code-LLMs, like Code4UIE and CodeKGC, utilize code-based schemas for more precise knowledge representation (Gan et al., 2023; Wei et al., 2023; Bi et al., 2024).
 

### 2024-11-05 paper/main.tex
Update main.tex
Related work section

--- 2024-11-05 paper/main.tex
@@
 \section{Related Work}
-\subsection{LLMs and Direct Webpage Information Extraction}
-Large Language Models (LLMs) have demonstrated remarkable abilities in replicating human-like task execution, particularly in web data extraction.
-Recent advancements have enabled LLMs to process entire web pages post-crawling, facilitating direct extraction of structured information such as product details and prices.
-This method capitalizes on the LLMs' capabilities to interpret complex HTML structures without manual rule-based configurations, enhancing adaptability across dynamic web environments (Ahluwalia et al., 2024).
-However, challenges remain, particularly in ensuring factual accuracy and avoiding excessive reliance on large, computationally intensive models (Xu et al., 2024).
-Despite these hurdles, this approach offers a promising alternative to traditional web scraping, as demonstrated by models like NeuScraper, which achieve improved accuracy by integrating neural networks for direct HTML text extraction (Xu et al., 2024).
-
-\subsection{LLMs and Webpage Content Simplification}
-An alternative approach to direct information extraction involves simplifying web content through LLMs before targeting specific data points.
-This method filters out redundant HTML elements, reducing the size and complexity of web data while retaining the relevant information for extraction.
-By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia \& Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023).
-Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).
-
+\subsection{Generative Information Extraction}
+Large Language Models (LLMs) are increasingly being used for generative information extraction (IE), where they directly generate structured knowledge from text—such as entities, relations, and events—offering an alternative to traditional discriminative methods (Xu et al., 2024).
+LLMs are especially advantageous in low-resource settings and support multitasking formats, which enhances their adaptability across various IE tasks.
+These tasks are typically categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with a rigorous comparison of models’ performance in each area (Xu et al., 2024).
+Recent universal IE frameworks employ both natural language-based LLMs (NL-LLMs) and code-based LLMs (Code-LLMs).
+NL-LLMs, like UIE and InstructUIE, use natural language prompts to generate structured information.
+In contrast, Code-LLMs, such as Code4UIE and CodeKGC, leverage code-based schemas, offering more precise knowledge representation (Gan et al., 2023; Wei et al., 2023; Bi et al., 2024).
+In addition to text-based IE, advancements in LLMs have facilitated information extraction from web data.
+These models now enable processing of entire web pages post-crawling, extracting structured information such as product details and prices without manual, rule-based configurations (Ahluwalia et al., 2024).
+This web data extraction capability utilizes LLMs’ proficiency in interpreting complex HTML structures, enhancing flexibility across dynamic online environments.
+However, challenges remain in ensuring factual accuracy and managing the computational demands of large models (Xu et al., 2024).
+Models like NeuScraper have addressed some of these challenges by integrating neural networks for direct HTML text extraction, yielding more accurate results and offering a promising alternative to traditional web scraping methods (Xu et al., 2024).
 \subsection{LLMs and XPaths for Information Extraction}
-Generating generalizable XPath queries using LLMs has emerged as a robust method for automating web information extraction across structurally similar websites.
-This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems.
+As a specific generation technique of large models, generating Xpath for web information retrieval is also an efficient method for automating web information extraction.
+This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems for structurally similar websites.
 Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
-This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (Huang et al., 2024).
-
+This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (AUTOSCRAPER, Huang et al., 2024).
+Specifically, AUTOSCRAPER employs a progressive generation phase to traverse HTML structures and a synthesis phase to refine reusable action sequences across similar web pages, enhancing scalability and efficiency in dynamic environments
 \begin{figure*}[h]

### 2024-11-07 scripts/benchmarks/swde.py
Update swde.py
sys.path.append('/Users/xxx/Documents/GitHub/FEILIAN')

@@ -10,6 +10,9 @@ from minify_html import minify
 from typing import Dict, List
 from collections import defaultdict
 
+#import sys
+#sys.path.append('/Users/brycewang/Documents/GitHub/FEILIAN')
+
 from dotenv import load_dotenv
 load_dotenv()
 

### 2024-11-11 paper/main.tex
Update main.tex
Updated Related works
update result and analysis

@@
+% !TEX root = C:\Users\xilua\My Drive\Workspace\llm_xpath\feilian\paper\main.tex
 \documentclass[a4paper]{article}
@@
 \and
-Hazul \\ Research Dept.\\
-                Science City, Sci 88088 \\ yvo@science.rdept.net
+Xinyu Luan \\ \\ \\ xinyuluan0320@gmail.com
 }
@@
 These tasks are typically categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with a rigorous comparison of models’ performance in each area (Xu et al., 2024).
+
 Recent universal IE frameworks employ both natural language-based LLMs (NL-LLMs) and code-based LLMs (Code-LLMs).
@@
 Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
+
 This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (AUTOSCRAPER, Huang et al., 2024).
@@
 
-...
+\subsection{Experimental Setup}
+
+\subsubsection{Models}
+We use DeepSeek and ChatGPT-4.0 as the primary large language models in our experiments.
+
+\subsubsection{Dataset}
+We use the SWDE \cite{abdin2024phi3technicalreporthighly} (Structured Web Data Extraction) dataset, which includes 90 of websites across 9 domains, in total 20414 web pages.
+
+\subsubsection{Experimental Parameters}
+We use DeepSeek-Chat as the main model for our XPath Agent. The Number of Seeds is 3 initial seeds are provided to guide query generation and the 
+Sample Size: 32 web pages are sampled per task to evaluate the model’s adaptability and generalizability.
+
+\subsection{Evaluation Metrics}
+For evaluation, we employ the metrics of precision, recall, F1 score, and accuracy. we utilized a set matching method to calculate the metrics 
+for multi-label classification tasks where the labels are unordered. 
+This involves comparing each predicted label set with the corresponding ground truth label set while disregarding the order of the labels. 
+First, Both the ground truth and predictions are converted into sets to ignore any order. Accuracy is then defined such that a prediction is 
+counted as correct if the predicted set exactly matches the ground truth set. We count correctly predicted labels as True Positives. 
+Incorrectly predicted labels that are not in ground truth are classified as False Positives, while the labels that should have been in predicted set 
+but were missed are designated as False Negatives. Additionally, since our data does not contain blank answers (with only a very few exceptions that have been removed), 
+our cases do not have true negatives. Finally, precision, recall, F1 score, and accuracy are calculated by the following formula.
+\begin{center}
+$presision=\frac{Ture Positives}{Ture Positives + False Positives}$\\ [0.3 cm]
+$recall=\frac{Ture Positives}{True Positives + False Negatives}$\\ [0.3 cm]
+$F1=\frac{2 \times precision \times recall}{precision + recall}$\\ [0.3 cm]
+$accuracy=\frac{True Positives}{True Positives + False Positives + False Negatives}$
+\end{center}
+
+\section{Results and Analysis}
+\subsection{Statistical Analysis}
+
+\begin{table}[ht]
+    \begin{center}
+    \caption{Experimental Results}
+
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
+    DeepSeek & 0.5794 & \textbf{0.6764} & 0.8017 & 0.7337 \\ 
+    GPT 4o & 0.5793 & 0.6423 & \textbf{0.8553} & 0.7336 \\
+    Claude 3.0 & 0.6091	& 0.6796 & 0.8546 & \textbf{0.7571} \\
+    Claude 3.5 & \textbf{0.6191} & \textbf{0.6916} & \textbf{0.8551} & \textbf{0.7647} \\ \hline
+    \end{tabular}
+    \end{center}
+    \end{table}
+
+    DeepSeek is strong in precision, making it good at avoiding irrelevant data. GPT 4o is highly effective at capturing a wide range of relevant content, 
+    ensuring that few important elements are missed. Claude 3.0 strikes a balanced approach, effectively combining both precision and recall for 
+    solid overall performance of F1 score. Claude 3.5 stands out as the most balanced and effective model, excelling across all key areas of accuracy, 
+    precision, recall, and overall performance. It provides the best mix of identifying relevant data while minimizing errors.
+
+\subsection{Comparative Analysis} 
+The AutoCrawler \cite{huang2024autoscraperprogressiveunderstandingweb} framework focuses on generating web crawlers for extracting specific information from semi-structured HTML. 
+It is designed with a two-phase approach: the first phase uses a progressive generation framework that leverages the hierarchical 
+structure of HTML pages, while the second phase employs a synthesis framework that improves crawler performance by learning from 
+multiple web pages.
+
+In comparison to XPath Agent, AutoCrawler presents a different approach, emphasizing a sequence of XPath actions rather than 
+just the extraction of XPath from snapshots. This difference may influence performance in various metrics, such as F1 score. 
+AutoCrawler's focus on refining action sequences based on learning from past errors might offer advantages in terms of robustness 
+and adaptability to dynamic web structures. However, your XPath Agent, by isolating XPath extraction tasks, might achieve greater 
+precision in structured environments where precise element identification is crucial.
+
+\subsection{Error Analysis} TODO
 

### 2024-11-11 paper/main.tex
update paper

@@
 \usepackage{caption} % 引入 caption 包
+\usepackage{hyperref}
+% \usepackage[sort, authoryear]{natbib}
 
+\bibliographystyle{plain} 
+% \setcitestyle{authoryear,open={(},close={)}}
 \captionsetup[figure]{skip=10pt} % 设置 caption 的下边距为 10pt
@@
 \author{
-Li Yu \\ \\ lijingyu68@gmail.com
+Yu Li \\ \\ lijingyu68@gmail.com
 \and
@@
 In this section, we present the methodology of our approach, which consists of two stages: Information Extraction (IE) and XPath Programming.
-The IE stage extracts target information from sanitized web pages, while the XPath Programming stage generates XPath queries based on the condensed html and extracted information.
+The IE stage extracts target information from sanitized web pages, while the XPath Programming stage generates XPath queries based on the condensed html by extracted information.
+The whole process based on seeded web pages, which is 3 in our implementation.
 Figure \ref{fig:workflow} illustrates the two-stage pipeline of XPath Agent.
@@
 Not like traditional IE, we discovered 2 key insights.
-Firstly, we prompt the LLM to not only extract questioned information but also include cue texts.
-Secondly, we sanitized the web page to reduce the complexity of the web page and make the LLM focus on the target information.
+Firstly, we prompt LLM not only extract questioned information but also cue texts.
+Secondly, we sanitized the web page to reduce the complexity of the web page and make the LLM focus on the target information with contextual semantic.
 
@@
 We designed an algorithm to sanitize the web page, which is shown in Algorithm \ref{alg:sanitizer}.
+We also employed minify-html\cite{minifyhtml} to further reduce the size of the web page.
 
@@
 It's efficient and can be easily implemented in any programming language.
-In our sampled web pages, the algorithm can help us reduce the size of the web page to 10\%~20\% on average.
+In our sampled web pages, it can help us reduce the size of the web page to 10\%~20\% on average.
 
 In our implementation, we prompt LLM to extract all information at once on a single page with JSON format.
-So, multiple fields can be extracted at the same time.
-Multiple values for a single field might be extracted.
-In this case, We simply treat all extracted values are relevant and passing them to the next stage.
+So, multiple fields or multiple values for a single field might be extracted.
+We treat all extracted values are relevant and passing them to the next stage.
 
@@
 
-\subsection{XPath Program}
+\subsection{Program XPath}
+
+Program XPath queries is a process to generate XPath queries based on the condensed html by extracted information.
+In order to let LLM have more context to program a robust XPath query, we condensed the html by the extracted information and prompt with 3 seeded web pages at once.
+The algorithm is shown in Algorithm \ref{alg:condenser}.
+
+The condenser based on the extracted information, which is the target information and cue texts.
+A distance function is used to identify the most relevant nodes so that we can keep them in the condensed html.
+During the condense process, we keep the target nodes and replace other nodes' children with "...".
 
@@
   \caption{HTML Condenser}
+  \label{alg:condenser}
   \KwIn{
@@
 \end{algorithm}
+
+\subsection{Static XPath Generation}
+
+Program a robust XPath query is a challenging task.
+Which requires to balance between rigidity and flexibility.
+The rigidity means the XPath query should strictly follow the specific structure of the web page.
+The flexibility means the XPath query should be pruned to be generalizable across different web pages.
+In our early experiments, we discovered that the XPath query generated by LLM is not sticky to the structure of the web page.
+So, we designed a static XPath generation algorithm to guide LLMs.
+
+The static XPath generation algorithm propagate from the target node to root node.
+It generates the XPath query in a bottom-up manner.
+Unlike naive XPath generation algorithm.
+We add more attributes (in our case, we include class and id) to the XPath query.
+It makes the XPath query richer.
+
+\subsection{Conversational XPath Evaluator}
+
+LLM are lacks of the environment to evaluate, correct or improve the XPath queries. So, we designed a evaluator to evaluate LLM generated XPath.
+
+The XPath evaluator is a function, which execute the XPath query on seeded web pages and feedback the result to LLM.
+The result include 3 parts: what are missing, what are redundant, and correctness of the XPath query.
+The LLM can based on feedback to improve the XPath query.
+
+In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result.
 
@@
 % \addbibresource{refs.bib}
-\bibliographystyle{plain} 
-\bibliography{refs}
+\bibliography{refs}{}
+
+\appendix
+
+\section{Information Extraction Prompt}
+This is the first appendix.
+
+\section{Program XPath Prompt}
+This is the second appendix.
 

### 2024-11-11 paper/main.tex
update table layout

@@
 
-\begin{table}[ht]
+\begin{table*}[h]
   \begin{center}
-    \caption{Experimental Results}
-
     \begin{tabular}{|c|c|c|c|c|}
@@
     \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
-    DeepSeek & 0.5794 & \textbf{0.6764} & 0.8017 & 0.7337 \\ 
+    DeepSeek V2.5 & 0.5794 & \textbf{0.6764} & 0.8017 & 0.7337 \\ 
     GPT 4o & 0.5793 & 0.6423 & \textbf{0.8553} & 0.7336 \\
@@
   \end{center}
-    \end{table}
+  \caption{Experimental Results}
+\end{table*}
 
-    DeepSeek is strong in precision, making it good at avoiding irrelevant data. GPT 4o is highly effective at capturing a wide range of relevant content, 
-    ensuring that few important elements are missed. Claude 3.0 strikes a balanced approach, effectively combining both precision and recall for 
-    solid overall performance of F1 score. Claude 3.5 stands out as the most balanced and effective model, excelling across all key areas of accuracy, 
-    precision, recall, and overall performance. It provides the best mix of identifying relevant data while minimizing errors.
+DeepSeek is strong in precision, making it good at avoiding irrelevant data.
+GPT 4o is highly effective at capturing a wide range of relevant content, ensuring that few important elements are missed.
+Claude 3.0 strikes a balanced approach, effectively combining both precision and recall for solid overall performance of F1 score.
+Claude 3.5 stands out as the most balanced and effective model, excelling across all key areas of accuracy, precision, recall, and overall performance.
+It provides the best mix of identifying relevant data while minimizing errors.
 
@@
 
-\subsection{Citations In Text}
-
-...
-
-\subsubsection{Footnotes}
-
-Indicate footnotes with a number\footnote{This is a sample footnote} in
-the text. Place the footnotes at the bottom of the page they appear on.
-Precede the footnote with a vertical rule of 2 inches (12 picas).
-
-\subsubsection{Figures}
-
-All artwork must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn artwork. Figure number and caption always appear after the
-the figure. Place one line space before the figure, one line space
-before the figure caption and one line space after the figure caption.
-The figure caption is initial caps and each figure is numbered
-consecutively.
-
-Make sure that the figure caption does not get separated from the
-figure. Leave extra white space at the bottom of the page to avoid
-splitting the figure and figure caption.
-
-Below is another figure using LaTeX commands.
-
-\subsubsection{Tables}
-
-All tables must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn tables. Table number and title always appear before the
-table.
-
-One line space before the table title, one line space after the table
-title and one line space after the table. The table title must be
-initial caps and each table numbered consecutively.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Sample Table}
-
-\bigskip
-
-\begin{tabular}{|l|l|r|}
-\hline
-A & B & 1\\ \hline
-C & D & 2\\
-E & F & 3\\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Handling References}
-
-Use a first level heading for the references. References follow the
-acknowledgements.
-
-\subsubsection{Acknowledgements}
-
-Use a third level heading for the acknowledgements. All acknowledgements
-go at the end of the paper.
-
 % \addbibresource{refs.bib}

### 2024-11-17 paper/main.tex
update introduction

@@
 \and
-Xinyu Luan \\ \\ \\ xinyuluan0320@gmail.com
+Xinyu Luan \\ \\ xinyuluan0320@gmail.com
 }
@@
 \begin{abstract}
-We introduce XPath Agent, a production-ready XPath programming agent tailored for web crawling tasks.
-A standout feature of XPath Agent is its capability to automatically program XPath queries from a set of sampled web pages.
-To illustrate its efficacy, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a suite of web crawling tasks.
-Our findings reveal that XPath Agent excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
-The well designed 2 stage pipelines makes it readily integrable into existing web crawling workflows, thereby saving time and effort in manual XPath query development.
+  We present XPath Agent, a production-ready XPath programming agent specifically designed for web crawling and web GUI testing.
+A key feature of XPath Agent is its ability to automatically generate XPath queries from a set of sampled web pages using a single natural language query.
+To demonstrate its effectiveness, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a range of web crawling tasks.
+Our results show that XPath Agent achieves comparable performance metrics while significantly reducing token usage and improving clock-time efficiency.
+The well-designed two-stage pipeline allows for seamless integration into existing web crawling or web GUI testing workflows, thereby saving time and effort in manual XPath query development.
 \end{abstract}
@@
 
-The advent of HTML5 \cite{TABARES2021101529} has introduced significant complexities to automated web scraping, exacerbating issues of fragmentation and protocol diversity that have long challenged the development of web standards.
+The advent of HTML5 \cite{TABARES2021101529} has introduced significant complexities to automated web scraping.
 These complexities stem from the enhanced capabilities and dynamic nature of HTML5, which require more sophisticated methods to accurately extract and interpret data.
-As traditional web scraping techniques struggle to keep pace with these advancements, there is a growing need for innovative solutions to navigate the intricacies of modern web technologies.
+To address these challenges, researchers have developed a variety of tools, such as Selenium \cite{selenium}.
+Which offers a set of application programming interfaces (APIs) to automate web browsers, enabling the extraction of data from web pages.
+However, program Selenium to extract data from web pages is a time-consuming and error-prone process.
+The most crucial part is how to locate the target information on the web page.
+XPath queries provide a solution to this problem by allowing users to navigate the HTML structure of a web page and extract specific elements.
+But, programming XPath queries is a challenging task, especially for non-technical users.
+
+In addition to web crawling, XPath is also essential for web GUI testing.
+Web GUI testing involves interacting with web elements to verify that the user interface behaves as expected.
+XPath queries are used to locate elements on a web page, such as buttons, input fields, and links, which are then interacted with during the testing process.
+By automating these interactions, testers can efficiently validate the functionality and appearance of web applications across different browsers and devices.
+The ability to generate accurate and robust XPath queries is crucial for ensuring comprehensive test coverage and reliable test results.
 
@@
 
-Instead of fine-tuning LLMs, AutoScraper\cite{huang2024autoscraperprogressiveunderstandingweb} adopt a simplified technique which involves traversing the webpage and constructing a final XPath using generated action sequences.
-By focusing on the hierarchical structure of HTML and leveraging similarities across different web pages, its significantly reduces the complexity and computational overhead.
+Instead of one time task execution, AutoScraper\cite{huang2024autoscraperprogressiveunderstandingweb} adopt a simplified technique which only involves text content of webpages.
+By focusing on the hierarchical structure of HTML and traversing the webpage, it construct a final XPath using generated action sequences.
+Such XPath is generalizable and can be applied to multiple webpages.
+Which significantly reduce the time required when execution.
 
-Scrolling, navigating, back and forward through webpages to program XPath queries is a nature way for human.
-But for LLM, this process is time-consuming and computationally expensive.
-We expect LLM can do better and efficient.
+But, the above approaches are not efficient in generating XPath queries.
+We introduced a more effective approach to generate XPath queries using LLMs which could simply integrate into existing web crawling or web GUI testing workflows.
 
@@
 Secondly, web pages are lengthy and complex, full of task unrelated information.
-Those information distract the LLMs from generating the correct XPath queries.
+Those information distract LLMs from generating the correct XPath queries.
 Thirdly, LLMs are context limited.
@@
 Which is a graph-based tool set which we can define the whole pipeline in a graph-based manner and execute it in parallel.
-Which significantly reduce the time required to generate XPath queries.
+Which significantly reduce the time to generate XPath queries.
 
@@
 
-We based each of the above motivations and make the following contributions:
+In summary, our contributions are as follows:
 
@@
 Models like NeuScraper have addressed some of these challenges by integrating neural networks for direct HTML text extraction, yielding more accurate results and offering a promising alternative to traditional web scraping methods (Xu et al., 2024).
+
 \subsection{LLMs and XPaths for Information Extraction}
-As a specific generation technique of large models, generating Xpath for web information retrieval is also an efficient method for automating web information extraction.
-This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems for structurally similar websites.
-Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
 
-This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (AUTOSCRAPER, Huang et al., 2024).
-Specifically, AUTOSCRAPER employs a progressive generation phase to traverse HTML structures and a synthesis phase to refine reusable action sequences across similar web pages, enhancing scalability and efficiency in dynamic environments
 \begin{figure*}[h]
@@
 \end{figure*}
+
+As a specific generation technique of large models, generating Xpath for web information retrieval is also an efficient method for automating web information extraction.
+This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems for structurally similar websites.
+Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
+
+This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (AUTOSCRAPER, Huang et al., 2024).
+Specifically, AUTOSCRAPER employs a progressive generation phase to traverse HTML structures and a synthesis phase to refine reusable action sequences across similar web pages, enhancing scalability and efficiency in dynamic environments.
 
@@
 
+\subsection{Static XPath Generation}
+
+Program a robust XPath query is a challenging task.
+Which requires to balance between rigidity and flexibility.
+The rigidity means the XPath query should strictly follow the specific structure of the web page.
+The flexibility means the XPath query should be pruned to be generalizable across different web pages.
+In our early experiments, we discovered that the XPath query generated by LLM is not sticky to the structure of the web page.
+So, we designed a static XPath generation algorithm to guide LLMs.
+
+The static XPath generation algorithm propagate from the target node to root node.
+It generates the XPath query in a bottom-up manner.
+Unlike naive XPath generation algorithm.
+We add more attributes (in our case, we include class and id) to the XPath query.
+It makes the XPath query richer.
+
+\subsection{Conversational XPath Evaluator}
+
+LLM are lacks of the environment to evaluate, correct or improve the XPath queries. So, we designed a evaluator to evaluate LLM generated XPath.
+
+The XPath evaluator is a function, which execute the XPath query on seeded web pages and feedback the result to LLM.
+The result include 3 parts: what are missing, what are redundant, and correctness of the XPath query.
+The LLM can based on feedback to improve the XPath query.
+
+In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result.
+
 \begin{algorithm}
@@
 \end{algorithm}
-
-\subsection{Static XPath Generation}
-
-Program a robust XPath query is a challenging task.
-Which requires to balance between rigidity and flexibility.
-The rigidity means the XPath query should strictly follow the specific structure of the web page.
-The flexibility means the XPath query should be pruned to be generalizable across different web pages.
-In our early experiments, we discovered that the XPath query generated by LLM is not sticky to the structure of the web page.
-So, we designed a static XPath generation algorithm to guide LLMs.
-
-The static XPath generation algorithm propagate from the target node to root node.
-It generates the XPath query in a bottom-up manner.
-Unlike naive XPath generation algorithm.
-We add more attributes (in our case, we include class and id) to the XPath query.
-It makes the XPath query richer.
-
-\subsection{Conversational XPath Evaluator}
-
-LLM are lacks of the environment to evaluate, correct or improve the XPath queries. So, we designed a evaluator to evaluate LLM generated XPath.
-
-The XPath evaluator is a function, which execute the XPath query on seeded web pages and feedback the result to LLM.
-The result include 3 parts: what are missing, what are redundant, and correctness of the XPath query.
-The LLM can based on feedback to improve the XPath query.
-
-In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result.
 

### 2024-11-17 feilian/agents/agent.py
update paper & dataset

@@ -195,11 +195,11 @@ def program_xpath_node(state: State):
         raw_html = minify(snippet["raw_html"], keep_closing_tags=True)
         tree = parse_html(raw_html)
 
-        field_object = snippet["data"].get(field_name, None)
+        field_object = snippet["data"].get(field_name, {})
         if not field_object:
             continue
 
-        values = field_object["value"]
+        values = field_object.get("value", [])
         if not values:
             continue
 
@@ -217,7 +217,7 @@ def program_xpath_node(state: State):
         if not target_xpath:
             continue
 
-        cue_text = field_object["cue_text"]
+        cue_text = field_object.get("cue_text", None)
         if os.environ.get("ABLATION_EXPERIMENT", None) == "WITHOUT_CUE":
             cue_text = None
         if cue_text:

### 2024-11-17 paper/main.tex
update paper & dataset
update paper

@@
 \usepackage{hyperref}
-% \usepackage[sort, authoryear]{natbib}
+\usepackage{tcolorbox}
+\usepackage{listings}
+\usepackage[utf8]{inputenc}
 
@@
 The well-designed two-stage pipeline allows for seamless integration into existing web crawling or web GUI testing workflows, thereby saving time and effort in manual XPath query development.
+The source code for XPath Agent is available at \url{https://github.com/eavae/feilian}.
 \end{abstract}
@@
 \subsection{Generative Information Extraction}
+
 Large Language Models (LLMs) are increasingly being used for generative information extraction (IE), where they directly generate structured knowledge from text—such as entities, relations, and events—offering an alternative to traditional discriminative methods (Xu et al., 2024).
@@
 We treat all extracted values are relevant and passing them to the next stage.
+The prompt for the Information Extraction stage is shown in Section \ref{sec:ie_prompt}.
 
@@
 
-In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result.
+In our implementation, we limited the number of feedback loop to 3.
+At the end of the loop, we take the best XPath query based on evaluation result as the final result.
+The prompt for the Program XPath stage is shown in Section \ref{sec:program_xpath_prompt}.
 
@@
 
-In comparison to XPath Agent, AutoCrawler presents a different approach, emphasizing a sequence of XPath actions rather than 
-just the extraction of XPath from snapshots. This difference may influence performance in various metrics, such as F1 score. 
+In comparison to XPath Agent, AutoCrawler presents a different approach, emphasizing a sequence of XPath actions rather than just the extraction of XPath from snapshots.
+This difference may influence performance in various metrics, such as F1 score.
 AutoCrawler's focus on refining action sequences based on learning from past errors might offer advantages in terms of robustness 
@@
 
+\clearpage
+\onecolumn
+
 \appendix
 
+\centerline{\Large\bfseries Appendix}
+
 \section{Information Extraction Prompt}
-This is the first appendix.
+\label{sec:ie_prompt}
+
+The prompt for the Information Extraction stage in the following format:
+
+\begin{tcolorbox}
+  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
+Extract the information and cues from the given context that are required by the question, and present the results in JSON format.
+When presenting the results, ensure character-level consistency with the extracted text, do not make any modifications.
+The given context may be incomplete or may not have the answer, so, the final JSON conclusion must not include any fields that have not been mentioned.
+
+When there are multiple similar expressions, prioritize them according to the following rules (from high to low):
+1. The label of the target text is more important in HTML semantics.
+2. The target text is completely within a tag, rather than within a sentence or paragraph.
+3. The target text is closer to other fields to be extracted.
+4. If these expressions can complement each other, please extract them all.
+
+Cue Text (cue_text, from high to low):
+1. Cue Text: In HTML, the indicative text that signals the upcoming extraction of the target text, such as `Phone number` or `Address:`.
+2. When there is no cue text, use an empty string.
+
+# Question:
+{{ query }}
+
+# Context:
+```html
+{{ context }}
+```
+
+# Answer Format (ignore the format requirements in the `Question`, strictly follow the answer format of cue_text and value):
+Thought: ...(Your thoughts, about fields mentioned in the context and their cues)...
+Conclusion: ...(Strictly follow the JSON example format to answer: {{ json_example }})...
+
+# Your Answer:
+\end{lstlisting}
+\end{tcolorbox}
 
 \section{Program XPath Prompt}
-This is the second appendix.
+\label{sec:program_xpath_prompt}
+
+The system prompt for the Program XPath stage in the following format:
+
+\begin{tcolorbox}
+  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
+You are a pro software engineer, your task is reading the HTML code that user sent, and then response **one** Xpath (wrapped in JSON) that can recognize the element in the HTML to extract `target value`.
+
+Here're some hints:
+1. Do not output the xpath with exact value or element appears in the HTML.
+2. Reference to the `target value` and the generated the xpath (if exists) to get more context.
+3. When using text predication, always using `contains(., 'value')` instead of `text()='value'`.
+4. If the target xpath ends with `text()[n]`, where n is not 1, please do not ignore it.
+5. If cue text exist, using cue text and cue xpath to compose a new xpath might be a better idea.
+6. String functions are allowed, such as `starts-with()`, `ends-with()`, `substring-before()`, `substring-after()`. Use it in caution, since it can only be used on `text()` node.
+
+Please always response in the following Json format:
+{
+  "thought": "", # a brief thought of how to confirm the value and generate the xpath
+  "xpath": "" # a workable xpath to extract the value in the HTML
+}    
+  \end{lstlisting}
+\end{tcolorbox}
+
+The feedback prompt for the Program XPath stage in the following format:
+
+\begin{tcolorbox}
+  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
+Following the feedbacks to refine the xpath you provided:
+
+1. Extend the xpath to include the missing information if `Missing`.
+2. Restrict the xpath to exclude the irrelevant information if `Surplus`.
+3. Correct the xpath grammer if `Invalid`.
+4. Response same xpath if no better solution.
+
+{% for feedback in feedbacks %}
+#### Evaluated on Fragment {{ feedback.id }}:
+Extracted (JSON encoded): `{{ feedback.extracted | tojson }}`
+Feedback Message: `{{ feedback.message }}`
+{%- endfor %}    
+  \end{lstlisting}
+\end{tcolorbox}
 

### 2024-11-29 paper/main.tex
Update related works section

@@
 \end{enumerate}
+\section{Related Work}
+Information extraction (IE) serves as a cornerstone of natural language processing, transforming unstructured text into structured entities, relations, and events.
+Traditional IE approaches often relied on task-specific models, which demanded substantial annotated corpora and computational resources.
+The advent of large language models (LLMs), particularly GPT-based architectures, has revolutionized this field.
+LLMs excel in zero-shot and few-shot learning due to pretraining on vast text corpora, enabling efficient and flexible IE for diverse and complex applications.
 
-\section{Related Work}
-\subsection{Generative Information Extraction}
+\subsection{Web Information Extraction}
 
-Large Language Models (LLMs) are increasingly being used for generative information extraction (IE), where they directly generate structured knowledge from text—such as entities, relations, and events—offering an alternative to traditional discriminative methods (Xu et al., 2024).
-LLMs are especially advantageous in low-resource settings and support multitasking formats, which enhances their adaptability across various IE tasks.
-These tasks are typically categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with a rigorous comparison of models’ performance in each area (Xu et al., 2024).
+Web information extraction (WebIE) has evolved alongside the increasing complexity of web layouts and dynamic content.
+Traditional rule-based methods, effective for static pages, struggle with modern web structures.
+LLMs and advanced frameworks have emerged as solutions, leveraging schema-based, multimodal, and generative techniques to unify tasks like Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE) through prompt engineering and fine-tuning \cite{xu2024largelanguagemodelsgenerative}.
 
-Recent universal IE frameworks employ both natural language-based LLMs (NL-LLMs) and code-based LLMs (Code-LLMs).
-NL-LLMs, like UIE and InstructUIE, use natural language prompts to generate structured information.
-In contrast, Code-LLMs, such as Code4UIE and CodeKGC, leverage code-based schemas, offering more precise knowledge representation (Gan et al., 2023; Wei et al., 2023; Bi et al., 2024).
-In addition to text-based IE, advancements in LLMs have facilitated information extraction from web data.
-These models now enable processing of entire web pages post-crawling, extracting structured information such as product details and prices without manual, rule-based configurations (Ahluwalia et al., 2024).
-This web data extraction capability utilizes LLMs’ proficiency in interpreting complex HTML structures, enhancing flexibility across dynamic online environments.
-However, challenges remain in ensuring factual accuracy and managing the computational demands of large models (Xu et al., 2024).
-Models like NeuScraper have addressed some of these challenges by integrating neural networks for direct HTML text extraction, yielding more accurate results and offering a promising alternative to traditional web scraping methods (Xu et al., 2024).
+Recent works emphasize the importance of modeling structural context in webpages.
+WebFormer \cite{wang2022webformerwebpagetransformerstructure} employs graph attention mechanisms to capture local and global dependencies within the DOM tree, achieving state-of-the-art results on the SWDE benchmark.
+Similarly, FreeDOM \cite{DBLP:journals/corr/abs-2010-10755} combines node-level encoding with pairwise relational features, enabling robust generalization across unseen websites without visual rendering.
+Simplified DOM representations, such as those used in SimpDOM \cite{zhou2021simplifieddomtreestransferable}, enhance feature transferability across verticals, achieving superior cross-domain performance while avoiding reliance on computationally expensive visual features.
 
-\subsection{LLMs and XPaths for Information Extraction}
+Generative approaches further demonstrate the adaptability of LLMs in WebIE.
+ChatIE \cite{wei2024chatie} reformulates extraction tasks into multi-turn dialogues, improving zero-shot capabilities.
+Frameworks like NeuScraper \cite{ahluwalia2024leveraginglargelanguagemodels} integrate neural models with HTML structures to enhance data quality, while MIND2WEB \cite{deng2023mind2webgeneralistagentweb} extends these innovations with a dataset and framework for training generalist agents capable of performing diverse tasks across real-world websites.
+
+On the multimodal front, models like GoLLIE \cite{sainz2024gollieannotationguidelinesimprove} and MoEEF \cite{yang2024hypertextentityextractionwebpage} integrate visual and textual data to address domain-specific challenges.
+GoLLIE aligns annotation guidelines with code generation for better extractions, while MoEEF incorporates hypertext features to boost entity recognition.
+Vision-based LLMs, such as GPT-4 Vision \cite{fellman-etal-2024-future}, highlight the growing importance of multimodal techniques for processing visually encoded web data.
+
+\subsection{LLMs and XPaths for Web Information Extraction}
+
+XPath, a language for querying hierarchical document structures, plays a vital role in bridging structured representation with computational modeling.
+MarkupLM \cite{DBLP:journals/corr/abs-2110-08518} demonstrates how XPath captures the genealogy of DOM nodes, seamlessly integrating textual and markup features for tasks such as Masked Markup Language Modeling (MMLM) and Node Relation Prediction (NRP).
+These techniques enable dynamic adaptation to complex web layouts, surpassing the limitations of 2D positional embeddings.
+
+XPath generation further extends WebIE capabilities.
+Tools like TREEX \cite{10.1145/3018661.3018740} and AUTOSCRAPER \cite{huang-etal-2024-autoscraper} employ decision tree learning and progressive HTML traversal to generate reusable extractors, balancing precision and recall for diverse applications such as price comparison and product aggregation.
+By leveraging the interpretive capabilities of LLMs, these methods scale to diverse web environments, underscoring the synergy between structured document analysis and scalable information extraction.
+
+\subsection{Summary}
+
+The evolution of WebIE reflects the integration of structural, multimodal, and generative techniques into scalable systems.
+LLMs and frameworks leveraging DOM structures, multimodal data, and XPath queries have significantly advanced this field, enabling robust and adaptable solutions for dynamic web environments.
+These advancements collectively highlight the transformative potential of combining pre-trained models, structural embeddings, and domain-specific optimizations in tackling modern WebIE challenges.
+Future directions should focus on enhancing generalization across unseen web domains and improving multimodal fusion for visually rich webpages.
 
@@
 \end{figure*}
-
-As a specific generation technique of large models, generating Xpath for web information retrieval is also an efficient method for automating web information extraction.
-This approach leverages LLMs’ understanding of document structures to create XPath queries that dynamically adapt to minor variations in web page layouts, increasing the scalability of extraction systems for structurally similar websites.
-Tools like TREEX, which integrate decision tree learning, allow for the synthesis of XPaths that balance precision and recall across multiple web pages, even those with unseen structures (Omari et al., 2024).
-
-This technique significantly reduces the need for manual intervention and facilitates the creation of highly efficient and reusable extractors for tasks such as price comparison and product aggregation across e-commerce platforms (AUTOSCRAPER, Huang et al., 2024).
-Specifically, AUTOSCRAPER employs a progressive generation phase to traverse HTML structures and a synthesis phase to refine reusable action sequences across similar web pages, enhancing scalability and efficiency in dynamic environments.
 

### 2024-12-01 feilian/datasets/__init__.py
add swde extended dataset

@@ -1,3 +1,3 @@
-from .dataset import SWDE, Dataset, Sample, Seed, SeedDataset
+from .dataset import SWDE, Dataset, Sample, Seed, SeedDataset, SWDEExpanded
 
-__all__ = ["SWDE", "Dataset", "Sample", "Seed", "SeedDataset"]
+__all__ = ["SWDE", "Dataset", "Sample", "Seed", "SeedDataset", "SWDEExpanded"]

### 2024-12-01 feilian/datasets/dataset.py

@@ -81,9 +81,7 @@ class SeedDataset:
             id=idx,
             query=df["query"].iloc[0],
             htmls=df["html"].tolist(),
-            ground_truth=[
-                json.loads(x) for x in df["ground_truth"].tolist()
-            ],
+            ground_truth=[json.loads(x) for x in df["ground_truth"].tolist()],
         )
 
     def __iter__(self):
@@ -97,6 +95,30 @@ class SWDE(Dataset):
         self.random_state = np.random.RandomState(seed)
 
         df = self.read_data()
+        seed_df = df.groupby(["category", "site"]).apply(
+            lambda x: x.sample(
+                n=3,
+                random_state=self.random_state,
+            )
+        )
+        drop_indices = set(i[2] for i in seed_df.index)
+        seed_df.reset_index(drop=True, inplace=True)
+        self.seed_df = seed_df
+        df: pd.DataFrame = df.drop(drop_indices)
+        df.reset_index(drop=True, inplace=True)
+
+        # sample in group category, site
+        df = (
+            df.groupby(["category", "site"])
+            .apply(
+                lambda x: x.sample(
+                    n=self.eval_sample_size,
+                    random_state=self.random_state,
+                ),
+            )
+            .reset_index(drop=True)
+        )
+        self.df = df
 
         # sample in group category, site
         df = (
@@ -128,21 +150,11 @@ class SWDE(Dataset):
         return categories
 
     def to_seed(self):
-        # sample 3 pages from each category, site
-        df = self.df.groupby(["category", "site"]).apply(
-            lambda x: x.sample(
-                n=3,
-                replace=True,
-                random_state=self.random_state,
-            )
-        )
-        df.reset_index(drop=True, inplace=True)
-
         # populate html and query
         ids = []
         htmls = []
         quries = []
-        for i, row in df.iterrows():
+        for i, row in self.seed_df.iterrows():
             category = row["category"]
             site = row["site"]
             page_id = row["page_id"]
@@ -275,3 +287,153 @@ class SWDE(Dataset):
                 )
             )
         return instances
+
+
+class SWDEExpanded(Dataset):
+    def __init__(self, data_folder: str, eval_sample_size: int, seed: int, swde_data_folder="../swde") -> None:
+        super().__init__(data_folder, eval_sample_size)
+        self.random_state = np.random.RandomState(seed)
+        self.swde_data_folder = os.path.join(data_folder, swde_data_folder)
+
+        df = self.read_data()
[…]

### 2024-12-02 paper/main.tex
Paper: To be submitted to ArXiv version.

@@
 \and
-Bryce Wang \\ Stanford University  \\ brycewang2018@gmail.com
+Bryce Wang\textsuperscript{*} \\ Stanford University  \\ brycewang2018@gmail.com
 \and
@@
 
-Web scraping \cite{khder2021web} automates data extraction from websites, vital for modern fields like Business Intelligence.
+Web scraping\cite{khder2021web} automates data extraction from websites, vital for modern fields like Business Intelligence.
 It excels in gathering structured data from unstructured sources like HTML, especially when machine-readable formats are unavailable.
@@
 
-The advent of HTML5 \cite{TABARES2021101529} has introduced significant complexities to automated web scraping.
+The advent of HTML5\cite{TABARES2021101529} has introduced significant complexities to automated web scraping.
 These complexities stem from the enhanced capabilities and dynamic nature of HTML5, which require more sophisticated methods to accurately extract and interpret data.
-To address these challenges, researchers have developed a variety of tools, such as Selenium \cite{selenium}.
+To address these challenges, researchers have developed a variety of tools, such as Selenium\cite{selenium}.
 Which offers a set of application programming interfaces (APIs) to automate web browsers, enabling the extraction of data from web pages.
@@
 But, programming XPath queries is a challenging task, especially for non-technical users.
-
-In addition to web crawling, XPath is also essential for web GUI testing.
-Web GUI testing involves interacting with web elements to verify that the user interface behaves as expected.
-XPath queries are used to locate elements on a web page, such as buttons, input fields, and links, which are then interacted with during the testing process.
-By automating these interactions, testers can efficiently validate the functionality and appearance of web applications across different browsers and devices.
-The ability to generate accurate and robust XPath queries is crucial for ensuring comprehensive test coverage and reliable test results.
 
@@
 GoLLIE aligns annotation guidelines with code generation for better extractions, while MoEEF incorporates hypertext features to boost entity recognition.
-Vision-based LLMs, such as GPT-4 Vision \cite{fellman-etal-2024-future}, highlight the growing importance of multimodal techniques for processing visually encoded web data.
+Vision-based LLMs, such as GPT-4 Vision\cite{fellman-etal-2024-future}, highlight the growing importance of multimodal techniques for processing visually encoded web data.
 
@@
 XPath, a language for querying hierarchical document structures, plays a vital role in bridging structured representation with computational modeling.
-MarkupLM \cite{DBLP:journals/corr/abs-2110-08518} demonstrates how XPath captures the genealogy of DOM nodes, seamlessly integrating textual and markup features for tasks such as Masked Markup Language Modeling (MMLM) and Node Relation Prediction (NRP).
+MarkupLM\cite{DBLP:journals/corr/abs-2110-08518} demonstrates how XPath captures the genealogy of DOM nodes, seamlessly integrating textual and markup features for tasks such as Masked Markup Language Modeling (MMLM) and Node Relation Prediction (NRP).
 These techniques enable dynamic adaptation to complex web layouts, surpassing the limitations of 2D positional embeddings.
@@
 XPath generation further extends WebIE capabilities.
-Tools like TREEX \cite{10.1145/3018661.3018740} and AUTOSCRAPER \cite{huang-etal-2024-autoscraper} employ decision tree learning and progressive HTML traversal to generate reusable extractors, balancing precision and recall for diverse applications such as price comparison and product aggregation.
+Tools like TREEX \cite{10.1145/3018661.3018740} and AUTOSCRAPER\cite{huang2024autoscraperprogressiveunderstandingweb} employ decision tree learning and progressive HTML traversal to generate reusable extractors, balancing precision and recall for diverse applications such as price comparison and product aggregation.
 By leveraging the interpretive capabilities of LLMs, these methods scale to diverse web environments, underscoring the synergy between structured document analysis and scalable information extraction.
@@
 These advancements collectively highlight the transformative potential of combining pre-trained models, structural embeddings, and domain-specific optimizations in tackling modern WebIE challenges.
-Future directions should focus on enhancing generalization across unseen web domains and improving multimodal fusion for visually rich webpages.
+Future directions should focus on enhancing generalization across unseen web domains and improving multimodal fusion for visually rich webpages efficiently.
 
@@
 \subsubsection{Dataset}
-We use the SWDE \cite{abdin2024phi3technicalreporthighly} (Structured Web Data Extraction) dataset, which includes 90 of websites across 9 domains, in total 20414 web pages.
+We use the SWDE\cite{abdin2024phi3technicalreporthighly} (Structured Web Data Extraction) dataset, which includes 90 of websites across 9 domains, in total 20414 web pages.
 
 \subsubsection{Experimental Parameters}
-We use DeepSeek-Chat as the main model for our XPath Agent. The Number of Seeds is 3 initial seeds are provided to guide query generation and the 
-Sample Size: 32 web pages are sampled per task to evaluate the model’s adaptability and generalizability.
+We use DeepSeek-Chat as the main model for our XPath Agent. The Number of Seeds is 3 initial seeds are provided to guide query generation with a  
+sample size of 32 web pages are sampled per task to evaluate the model’s adaptability and generalizability.
 
@@
     \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
-    DeepSeek V2.5 & 0.5794 & \textbf{0.6764} & 0.8017 & 0.7337 \\ 
-    GPT 4o & 0.5793 & 0.6423 & \textbf{0.8553} & 0.7336 \\
-    Claude 3.0 & 0.6091	& 0.6796 & 0.8546 & \textbf{0.7571} \\
-    Claude 3.5 & \textbf{0.6191} & \textbf{0.6916} & \textbf{0.8551} & \textbf{0.7647} \\ \hline
+    DeepSeek V2.5 & 0.5794 & 0.6764 & 0.8017 & 0.7337 \\ 
+    GPT 4o mini & 0.6613 &0.8056 &0.7868 &0.7961 \\
+    GPT 4o      &\textbf{0.7413} &\textbf{0.8561} &0.8467 &\textbf{0.8514} \\
+    Claude 3.5  & 0.6191 & 0.6916 & \textbf{0.8551} & 0.7647 \\ \hline
     \end{tabular}
@@
 \subsection{Comparative Analysis} 
-The AutoCrawler \cite{huang2024autoscraperprogressiveunderstandingweb} framework focuses on generating web crawlers for extracting specific information from semi-structured HTML. 
+The AutoCrawler\cite{huang2024autoscraperprogressiveunderstandingweb} framework focuses on generating web crawlers for extracting specific information from semi-structured HTML. 
 It is designed with a two-phase approach: the first phase uses a progressive generation framework that leverages the hierarchical 

### 2024-12-22 paper/main.tex
add gemini result and add stats in the paper

@@
 \usepackage[utf8]{inputenc}
+\usepackage{colortbl}
 
@@
 \begin{table*}[h]
-  \begin{center}
-    \begin{tabular}{|c|c|c|c|c|}
+  % \begin{center}
+  \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
     \hline
-    \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
-    DeepSeek V2.5 & 0.5794 & 0.6764 & 0.8017 & 0.7337 \\ 
-    GPT 4o mini & 0.6613 &0.8056 &0.7868 &0.7961 \\
-    GPT 4o      &\textbf{0.7413} &\textbf{0.8561} &0.8467 &\textbf{0.8514} \\
-    Claude 3.5  & 0.6191 & 0.6916 & \textbf{0.8551} & 0.7647 \\ \hline
+    \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} & \textbf{Correct} & \textbf{Precision} & \textbf{Recall} & \textbf{F1}\\ \hline
+    \multicolumn{5}{|c|}{\cellcolor{yellow!30}Xpath Agent} & \multicolumn{4}{|c|}{\cellcolor{cyan!20} Auto Scraper}\\ \hline
+    Deepseek V2.4       & 0.6312 & 0.7484 & 0.8012 & 0.7739       & & & &  \\
+    DeepSeek V2.5       & 0.5794 & 0.6764 & 0.8017 & 0.7337       & & & & \\ 
+    GPT 4o mini         & 0.6613 & 0.8056 & 0.7868 & 0.7961       & 0.6206 & 0.9176 & 0.7810 & 0.7697 \\
+    GPT 4o              &\textbf{0.7413} &\textbf{0.8561} &0.8467 &\textbf{0.8514}            & & & & \\
+    GPT 3.5 Turbo       & & & &                                   & 0.5484 & 0.8585 & 0.7334 & 0.6920 \\
+    GPT 4.0 Turbo       & & & &                                   & 0.7156 & 0.9249 & 0.8913 & 0.8869 \\
+    Claude 3-5 haiku    & 0.6123 & 0.6845 & 0.8530 & 0.7595       & & & & \\
+    Claude 3-5 sonnet   & 0.6191 & 0.6916 & 0.8551 & 0.7647       & & & & \\
+    Claude 3 opus       & 0.6112 & 0.6838 & 0.8520 & 0.7587       & & & & \\
+    Claude 3 sonnet     & 0.6091 & 0.6796 & 0.8546 & 0.7571       & & & & \\
+    Gemini 1.5 flash    & 0.3746 & 0.4152 & 0.7930 & 0.5450       & & & & \\
+    Gemini 1.5 pro      & 0.6306 & 0.7454 & 0.8037 & 0.7735       & 0.4281 & 0.8570 & 0.5754 & 0.7491 \\
+
+    \hline
     \end{tabular}
-  \end{center}
+
   \caption{Experimental Results}
